Emulation of high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2022-11-04 paper1.tex
fix typos

The generated phase-space points are fed to the {\NJet} package \cite{Badger:2012pg} to calculate colour and helicity summed tree-level matrix elements. 
All external legs have been considered to be massless. 
The strong coupling constant has been set to $\alpha_{s} = 0.118$, and the electromagnetic coupling constant has been set to $\alpha_{e} = 1.0 / 132.5070$.
The mass of the $Z$-boson is taken to be $m_{Z} = 91.188$ GeV.
These parameters and those not listed, are consistent with those in the Standard Model mode of \aNLO \cite{Alwall_2014}.

@@

\begin{table}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Region & $y_{\mathrm{cut}}$ & Fraction of pts & Pts outside $0.1\%$ & Pts outside $1\%$ & Pts outside $5\%$ \\
        \hline
        \multirow{3}{*}{White} & 0.01   & 36.5\% & 1.9\% & 0.0\% & 0.0\% \\
        \cline{2-6}
                               & 0.001  & 74.8\% & 0.98\% & 0.0\% & 0.0\% \\
        \cline{2-6}
                               & 0.0001 & 78.4\% & 1.9\% & 0.0\%  & 0.0\% \\
        \hline
        \hline
        \multirow{3}{*}{Pink}  & 0.01   & 27.6\% & 58.2\% & 25.2\% & 12.9\% \\
        \cline{2-6}
                               & 0.001  & 13.5\% & 31.7\% & 6.5\% & 0.53\% \\
        \cline{2-6}
                               & 0.0001 & 13.5\% & 38.9\% & 9.3\% & 2.8\% \\
        \hline
        \hline
        \multirow{3}{*}{Purple}& 0.01   & 7.2\% & 69.1\% & 32.1\% & 20.3\% \\
        \cline{2-6}
                               & 0.001  & 3.6\% & 31.3\% & 7.9\% & 4.5\% \\
        \cline{2-6}
                               & 0.0001 & 3.6\% & 30.5\% & 1.6\% & 0.0\% \\
        \hline
        \hline
        \multirow{3}{*}{Blue}  & 0.01   & 1.5\% & 79.3\% & 41.6\% & 0.77\% \\
        \cline{2-6}
                               & 0.001  & 0.4\% & 29.2\% & 0.0\% & 0.0\% \\
        \cline{2-6}
                               & 0.0001 & 0.4\% & 76.4\% & 0.0\% & 0.0\% \\
        \hline
        \hline
        \multirow{3}{*}{Red}   & 0.01   & 52.5\% & 76.2\% & 38.6\% & 20.5\% \\
        \cline{2-6}
                               & 0.001  & 7.0\%  & 69.9\% & 25.2\% & 9.5\% \\
        \cline{2-6}
                               & 0.0001 & 1.1\%  & 90.8\% & 33.8\% & 1.5\% \\
        \hline
    \end{tabular}
    \caption{The performance of trajectory predictions separated for white, pink, purple, blue, and red regions.
    We present the percentage of points that lie outside 0.1\%/1.0\%/5.0\% errors.
    Fraction of points indicates the percentage of points that lie in the region of interest, out of all phase-space points from the 50 trajectories we examine.
    }
    \label{table:trajectory_predictions}
\end{table}

>>>>

The generated phase-space points are fed to the {\NJet} package \cite{Badger:2012pg} to calculate colour and helicity summed tree-level matrix elements. 
All external legs have been considered to be massless. 
The strong coupling constant has been set to $\alpha_{s} = 0.118$, and the electromagnetic coupling constant has been set to $\alpha_{e} = 1.0 / 132.5070$.
The mass of the $Z$-boson is taken to be $m_{Z} = 91.188$ GeV.
These parameters and those not listed, are consistent with those in the Standard Model mode of \aNLO \cite{Alwall:2014hca}.

@@

\begin{table}
    \centering
    \small
    \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Region & $y_{\mathrm{cut}}$ & Frac. of pts & Pts outside $0.1\%$ & Pts outside $1\%$ & Pts outside $5\%$ \\
        \hline
        \multirow{3}{*}{White} & 0.01   & 36.5\% & 1.9\% & 0.0\% & 0.0\% \\
        \cline{2-6}
                               & 0.001  & 74.8\% & 0.98\% & 0.0\% & 0.0\% \\
        \cline{2-6}
                               & 0.0001 & 78.4\% & 1.9\% & 0.0\%  & 0.0\% \\
        \hline
        \hline
        \multirow{3}{*}{Pink}  & 0.01   & 27.6\% & 58.2\% & 25.2\% & 12.9\% \\
        \cline{2-6}
                               & 0.001  & 13.5\% & 31.7\% & 6.5\% & 0.53\% \\
        \cline{2-6}
                               & 0.0001 & 13.5\% & 38.9\% & 9.3\% & 2.8\% \\
        \hline
        \hline
        \multirow{3}{*}{Purple}& 0.01   & 7.2\% & 69.1\% & 32.1\% & 20.3\% \\
        \cline{2-6}
                               & 0.001  & 3.6\% & 31.3\% & 7.9\% & 4.5\% \\
        \cline{2-6}
                               & 0.0001 & 3.6\% & 30.5\% & 1.6\% & 0.0\% \\
        \hline
        \hline
        \multirow{3}{*}{Blue}  & 0.01   & 1.5\% & 79.3\% & 41.6\% & 0.77\% \\
        \cline{2-6}
                               & 0.001  & 0.4\% & 29.2\% & 0.0\% & 0.0\% \\
        \cline{2-6}
                               & 0.0001 & 0.4\% & 76.4\% & 0.0\% & 0.0\% \\
        \hline
        \hline
        \multirow{3}{*}{Red}   & 0.01   & 52.5\% & 76.2\% & 38.6\% & 20.5\% \\
        \cline{2-6}
                               & 0.001  & 7.0\%  & 69.9\% & 25.2\% & 9.5\% \\
        \cline{2-6}
                               & 0.0001 & 1.1\%  & 90.8\% & 33.8\% & 1.5\% \\
        \hline
    \end{tabular}
    \caption{The performance of trajectory predictions separated for white, pink, purple, blue, and red regions.
    We present the percentage of points that lie outside 0.1\%/1.0\%/5.0\% errors.
    Fraction of points indicates the percentage of points that lie in the region of interest, out of all phase-space points from the 50 trajectories we examine.
    }
    \label{table:trajectory_predictions}
\end{table}
